Sorting algorithms: how are they affected by memory faults?

### 2019-12-20 paper/Background.tex

In this section, we'll provide some definitions of memory faults and used sorting algorithms.

\subsection{Memory Faults}

Despite the title of this subsection, when the entire digital system (or software) is considered, there are three terms for computing fault and they have different meanings: failure, fault and error.

A failure denotes an element's inability to perform its functions because of error in the element itself or its environment. A fault is an anomalous physical condition. Causes include design errors, manufacturing problems, damage, fatigue, or other deterioration. Faults resulting from design errors and external factors are especially difficult to model and protect against because their occurrences and effects are hard to predict. An error is a manifestation of a fault in a system, in which the logical state of an element differs from its intended value. A fault in a system does not necessarily result in an error. An error occurs for a particular system state and input when an incorrect next state and/or output results \cite{Nelson1990}.

>>>>

In this section we describe basic concepts about memory faults and sorting algorithms.

\input{MemoryFaults}

\input{SortingAlgorithms}

### 2019-12-20 paper/SortingAlgorithms.tex

\section{Sorting Algorithms}

@@

\subsection{Quicksort}

@@

\subsection{Mergesort}

@@

\subsection{Insertionsort}

@@

\subsection{Bubblesort}

The bubble sort is the oldest and simplest sorting method in use. It works by comparing each item in the list with the item next to it, and swapping them if required. The algorithm repeats this process until it makes a pass all the way through the list without swapping any items (in other words, all items are in the correct order) \cite{Mansotra2011}.

>>>>

\subsection{Sorting Algorithms}

@@

\subsubsection{Quicksort}

@@

\subsubsection{Mergesort}

@@

\subsubsection{Insertionsort}

@@

\subsubsection{Bubblesort}

The bubble sort is the oldest and simplest sorting method in use. It works by comparing each item in the list with the item next to it, and swapping them if required. The algorithm repeats this process until it makes a pass all the way through the list without swapping any items (in other words, all items are in the correct order) \cite{Mansotra2011}.\\
